Model Order Redcution of Fluid Flow While Preserving Quadratic Invariants

### 2018-07-12 sections/5.res.tex
Picture for Kelvin-Helmholtz example

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%% Snapshots of KH %%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[h!]
\includegraphics[scale=0.115]{data/Compressible_Euler/KH/Snapshots/density_200_307.png}\hspace{1em}
\includegraphics[scale=0.115]{data/Compressible_Euler/KH/Snapshots/density_500_307.png}\hspace{1em}
\includegraphics[scale=0.115]{data/Compressible_Euler/KH/Snapshots/density_exact_307.png}\\

\includegraphics[scale=0.115]{data/Compressible_Euler/KH/Snapshots/density_200_461.png}\hspace{1em}
\includegraphics[scale=0.115]{data/Compressible_Euler/KH/Snapshots/density_500_461.png}\hspace{1em}
\includegraphics[scale=0.115]{data/Compressible_Euler/KH/Snapshots/density_exact_461.png}\\

\includegraphics[scale=0.115]{data/Compressible_Euler/KH/Snapshots/density_200_614.png}\hspace{1em}
\includegraphics[scale=0.115]{data/Compressible_Euler/KH/Snapshots/density_500_614.png}\hspace{1em}
\includegraphics[scale=0.115]{data/Compressible_Euler/KH/Snapshots/density_exact_614.png}\\

\includegraphics[scale=0.115]{data/Compressible_Euler/KH/Snapshots/density_200_768.png}\hspace{1em}
\includegraphics[scale=0.115]{data/Compressible_Euler/KH/Snapshots/density_500_768.png}\hspace{1em}
\includegraphics[scale=0.115]{data/Compressible_Euler/KH/Snapshots/density_exact_768.png}

\caption{Solutions of the Kelvin-Helmholtz problem at $t=\left\{ 0.4, 0.6, 0.8, 1 \right\}$. From left to right we have the solution of the reduced model with $k=200$, $k=500$ and the high fidelity solution.}
\label{fig:snap_solution_incompressible_Euler}
\end{figure}
